Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-05 paper/paper.tex
review abstract by Abate

\maketitle
\begin{abstract}
Modern control systems are by and large implemented in digital microcontrollers. This poses a new dimension to the problem of correct by design controllers which do not only need to look at the dynamics involved, but also at the effects of digitalization. This is particularly true in small size implementations where the effects of word length are significant with respect to the dynamics.
This work focuses on the synthesis of digital controllers for Linear Time Invariant SISO systems. We explore the effects of digitalization of the continuous signals and Fixed Word Length (FWL) in the controller dynamics.
To this end we propose a CEGIS solution that uses inductive invariant synthesis in conjunction with a digital stability verification algorithm from a well known tool to find a parametric solution for a digital controller given a model specification. The algorithm factors in quantization errors, sample and hold behaviour, and parameter representation round-offs.
The results show...
\end{abstract}

@@

\keywords{Control Synthesis, CEGIS, FWL}

@@

Next, the following Jury matrix
$M = [m_{ij}]_{(2N−2)\times N}$ is built from $S(z)$ coefficients:
%
$$
M=\left( 
\begin{array}{c}
V^{(0)}\\
V^{(1)}\\
\vdots\\
V^{(N-2)}
\end{array}
\right)
$$
%
where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ such that:
%
$$
v_{ij}^{(0)}=\left\{
\begin{array}{ll}
a_{j-1}, & \texttt{if}~i=1\\
v_{(1)(N-j+1)}^{0},&\texttt{if}~i=2
\end{array}
\right.
$$
%
$$
v_{ij}^{(k)}=\left\{
\begin{array}{ll}
0,&\texttt{if}~j>n-k\\
v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \texttt{if}~j\leq n-k ~\texttt{and}~i=1\\
v_{(1)(N-j+1)}^{k},& \texttt{if}~j\leq n-k ~\texttt{and}~i=2\\
\end{array}
\right.
$$
%
where $k \in \mathbb{Z}$, such that $0 < k < N − 2$. 
$S(z)$ is the
characteristic polynomial of a stable system if and only if
the following four propositions hold:
\begin{itemize}
\item $R_1: S(1) > 0$;
\item $R_2: (−1)^N S(−1) > 0$;
\item $R_3: |a_0| < a_N$;
\item $R_4: m_{11} > 0 \equiv m_{31} \wedge m_{51} \wedge \cdots \wedge m_{(2N−3)(1)}$.
\end{itemize}

The stability property is then encoded by creating a
constraint of the form:
$$\phi_{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4)$$
\cdsay{figure out what is existentially quantified for the final $\sigma$.}

@@

>>>>

\maketitle
\begin{abstract}
Modern control systems are by and large implemented via digital microcontrollers, 
which are designed to work in an embedded environment, 
within a dynamical plant that can present physical components. 
%
This poses a new dimension to the problem of controllers synthesis,   
which is classically studied in digital control literature. 
%
In this study, we plan to provide a principled approach to extend this literature in a number of directions: 
we are interested in quantitative tasks;  
we focus on automated correct-by-design synthesis algorithms, as opposed to verification objectives; 
and we encompass the compete range of approximations, related to time discretisation, quantisation effects, 
and finite-precision representations (with related rounding errors). To this end, 
we propose a CEGIS-based solution that uses inductive invariant synthesis in conjunction with a digital verification algorithm 
to find a parametric solution for a digital controller given a continuous plant specification. 
\end{abstract}

@@

\keywords{Control synthesis, CEGIS, finite word length, time sampling, quantisation, interval analysis}

@@

Next, the following Jury matrix
$M = [m_{ij}]_{(2N−2)\times N}$ is built from $S(z)$ coefficients:
%
$$
M=\left( 
\begin{array}{c}
V^{(0)}\\
V^{(1)}\\
\vdots\\
V^{(N-2)}
\end{array}
\right)
$$
%
where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ such that:
%
$$
v_{ij}^{(0)}=\left\{
\begin{array}{ll}
a_{j-1}, & \texttt{if}~i=1\\
v_{(1)(N-j+1)}^{0},&\texttt{if}~i=2
\end{array}
\right.
$$
%
$$
v_{ij}^{(k)}=\left\{
\begin{array}{ll}
0,&\texttt{if}~j>n-k\\
v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \texttt{if}~j\leq n-k ~\texttt{and}~i=1\\
v_{(1)(N-j+1)}^{k},& \texttt{if}~j\leq n-k ~\texttt{and}~i=2\\
\end{array}
\right.
$$
%
where $k \in \mathbb{Z}$, such that $0 < k < N − 2$. 
$S(z)$ is the
characteristic polynomial of a stable system if and only if
the following four propositions hold:
\begin{itemize}
\item $R_1: S(1) > 0$;
\item $R_2: (−1)^N S(−1) > 0$;
\item $R_3: |a_0| < a_N$;
\item $R_4: m_{11} > 0 \wedge m_{31}>0 \wedge m_{51}>0 \wedge \cdots \wedge m_{(2N{-}3)(1)}>0$.
\end{itemize}

The stability property is then encoded by creating a
constraint of the form:
$$\phi_{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4)$$
%\cdsay{figure out what is existentially quantified for the final $\sigma$.}
If the system is unstable,
i.e. if $\neg \phi_{stability}$ is satisfiable for $S(z)$, then the {\sc verify}
phase will provide values for each coefficients of $\hat{N_{G}(z)}$ and $\hat{D_{G}(z)}$,
which make the closed-loop system unstable.

@@

% <a>
% <item>7.515781402587890625</item>
% <item>-4.385616302490234375</item>
% <item>4.142093658447265625</item>
% </a>
% <a_size>3</a_size>
% <b>
% <item>-3.52398681640625</item>
% <item>-1.530254364013671875</item>
% <item>7.58094024658203125</item>
% </b>
% <b_size>3</b_size>
